---
title: "Donald Kane"
output: html_document
---

Find the correlation between energy consumption, production and expenditures and use scatterplot with a regression line to show the relationship. (scatterplot)

Use U.S. maps to show the consumption and expenditures of coal, petroleum, etc. Find each state’s consumption to GDP correlation. (US map plots, scatterplots, correlation)

Show distribution of energy consumption (bar graph)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
Energy_Census_and_Economic_Data_US_2010_2014 <- read_csv("Energy Census and Economic Data US 2010-2014.csv")
View(Energy_Census_and_Economic_Data_US_2010_2014)
```

```{r message=FALSE, warning=FALSE}
install.packages("usmap")
library(usmap)
library(ggplot2)
```

``` {r}
colnames(Energy_Census_and_Economic_Data_US_2010_2014)[2] <- "state"

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalC10-11", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2010 and 2011 in Total Energy Consumption"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalC11-12", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2011 and 2012 in Total Energy Consumption"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalC12-13", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2012 and 2013 in Total Energy Consumption"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalC13-14", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2013 and 2014 in Total Energy Consumption"
  )
```

```{r}
plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalP10-11", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2010 and 2011 in Total Energy Production"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalP11-12", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2011 and 2012 in Total Energy Production"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalP12-13", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2012 and 2013 in Total Energy Production"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalP13-14", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2013 and 2014 in Total Energy Production"
  )
```

```{r}
plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalPrice10-11", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2010 and 2011 in Total Energy Price"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalPrice11-12", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2011 and 2012 in Total Energy Price"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalPrice12-13", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2012 and 2013 in Total Energy Price"
  )

plot_usmap(data = Energy_Census_and_Economic_Data_US_2010_2014, values = "TotalPrice13-14", color = "red") + 
  scale_fill_continuous(name = "Coal", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(
    title = "Percent Change Between 2013 and 2014 in Total Energy Price"
  )
```



```{r}
Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalC10-11`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "red") + 
  theme_classic() + 
  labs(
    title = "Total Energy Consumption in Billion BTU 2010 - 2011",
    x = "Energy Consumption in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalC11-12`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "red") +
  theme_classic() + 
  labs(
    title = "Total Energy Consumption in Billion BTU 2011 - 2012",
    x = "Energy Consumption in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalC12-13`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "red") +
  theme_classic() + 
  labs(
    title = "Total Energy Consumption in Billion BTU 2012 - 2013",
    x = "Energy Consumption in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalC13-14`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "red") +
  theme_classic() + 
  labs(
    title = "Total Energy Consumption in Billion BTU 2013 - 2014",
    x = "Energy Consumption in Billion BTU"
  )
```

```{r}
Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalP10-11`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 2.5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "blue") + 
  theme_classic() + 
  labs(
    title = "Total Energy Production in Billion BTU 2010 - 2011",
    x = "Energy Production in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalP11-12`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 2.5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "blue") +
  theme_classic() + 
  labs(
    title = "Total Energy Production in Billion BTU 2011 - 2012",
    x = "Energy Production in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalP12-13`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 2.5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "blue") +
  theme_classic() + 
  labs(
    title = "Total Energy Production in Billion BTU 2012 - 2013",
    x = "Energy Production in Billion BTU"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalP13-14`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 2.5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "blue") +
  theme_classic() + 
  labs(
    title = "Total Energy Production in Billion BTU 2013 - 2014",
    x = "Energy Production in Billion BTU"
  )
```

```{r}
Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalPrice10-11`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "green") + 
  theme_classic() + 
  labs(
    title = "Total Energy Average Price in USD Million BTU in 2010 - 2011",
    x = "Average Price in Millions"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalPrice11-12`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "green") +
  theme_classic() + 
  labs(
    title = "Total Energy Average Price in USD Million BTU in 2011 - 2012",
    x = "Average Price in Millions"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalPrice12-13`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "green") +
  theme_classic() + 
  labs(
    title = "Total Energy Average Price in USD Million BTU in 2012 - 2013",
    x = "Average Price in Millions"
  )

Energy_Census_and_Economic_Data_US_2010_2014 %>%
  ggplot(aes(`TotalPrice13-14`)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = .5, color = "black", fill = "gray") +
  geom_density(alpha = 0.5, fill = "green") +
  theme_classic() + 
  labs(
    title = "Total Energy Average Price in USD Million BTU in 2013 - 2014",
    x = "Average Price in Millions"
  )
```













