---
title: "gdp"
author: "Anubha Nagar"
date: "28/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#library(ggdemetra)
library(tidyverse)
library(ggplot2)
library(ggpubr)
```

```{r}
data <- read_csv("Energy Census and Economic Data US 2010-2014.csv")
```

```{r}
head(data)
str(data)
```
```{r}
data=na.omit(data)
```

```{r}
#Filter data for gdp
data<-data%>%
  select("StateCodes","State","Region","Division","Coast", "GDP2010", "GDP2011", "GDP2012", "GDP2014")%>%
  pivot_longer(c("GDP2010", "GDP2011", "GDP2012", "GDP2014"), names_to = "Year", values_to = "gdp")
#Clean Year BiomassC
data$Year<-gsub("GDP","",as.character(gdp$Year))
#Display the outcome
data
```


# understanding the increase in gdp over time in the US 

```{r}
overall_gdp <- data%>% 
  group_by(Year)%>%
  summarize(n = sum(gdp))
overall_gdp
```
plotting the increase in gdp 
```{r}
install.packages("hrbrthemes")
```

```{r}
library(hrbrthemes)
ggplot(overall_gdp,aes(x = Year, y = n))+ geom_point()+
geom_line( color="grey") +
    geom_point(shape=21, color="black", fill="#69b3a2", size=6) +
    theme_ipsum() +
    ggtitle("Change in GDP over the years 2010- 2014")
```

Yearly boxplot for top 5 state with highest gdp 

```{r}
top5_states <- data%>%
  group_by(State)%>%
  summarize(n = sum(gdp))%>%
  arrange(desc(n))%>%
  slice(1:5)
```

California, Texas, NY, Florida and Illinois has the highest cumulative GDP (2010- 2014)

Now lets plot boxplots to understand the trend in gdp

```{r}
#graph1 <- par(mfrow= c(2,2))
plot_cali <- data%>%
  filter(State == "California"| State == "Texas"|State == "New York"| State == "Illinois"|State == "Florida")
  ggplot(plot_cali, aes(x = Year, y = gdp))+ geom_point(aes(col = State))

```

#Lets understand if the GDP of the state is above the mean gdp of US
for 2010

```{r}
mean_gdp <- data%>%
  filter(Year== 2010)%>%
  summarize(mean = (sum(gdp)/51))
mean_gdp
```
```{r}
data <- data%>%
  mutate(diff_from_mean = gdp - 291368.1)
```

```{r}
# install.packages("ggplot2")
library(ggplot2)

ggplot(data, aes(x = reorder(StateCodes,diff_from_mean ), y = diff_from_mean)) +
  geom_bar(stat = "identity",
           show.legend = FALSE, fill = "lightblue") +
  xlab("Group") +
  ylab("Value") +
  coord_flip() 

```

Try changing color and reduce size of states
and scale of x axis 

Now lets analyze if the disparity in GDP for the different regions of US

```{r}
nsew <- data%>%
  group_by(Region)%>%
  summarize(mean_gdp_region = mean(gdp))
```

plot bar plot to see the same 
northern states are doing the best in terms of gdp (change y axis labels)
label 1 as North 
and so on
```{r}
ggplot(nsew, aes(x = Region, y = mean_gdp_region))+ geom_bar(stat = "identity", fill = "Purple", alpha = 0.4)
```

which state has the greatest gdp increase?

```{r}
data2010 <- data%>%
  filter(Year == 2010)%>%
  select(StateCodes,gdp)
data2014 <- data%>%
  filter(Year == 2014)%>%
  select(StateCodes,gdp)
```

```{r}
df <- merge(x=data2010,y=data2014,by="StateCodes",all=TRUE)
df <- df%>%
  mutate(diff = gdp.y- gdp.x)%>%
  arrange(desc(diff))%>%
  slice(1:5)
df


```
Here we see the same states have the greatest increase in gdp as well as the mean gdp 

```{r}
ggplot(df, aes(x = StateCodes, y = diff))+ geom_bar(stat = "identity", fill = "lightblue")
```

